Trees

### 2019-01-28 Trees_making.Rmd
fixed tree saving and reading

```{r check Curtis1998 tree binary}
is.binary.tree(tree) #FALSE (i.e. there are polytomies)
# is.ultrametric(tree) #the tree has no branch lengths, so cant be checked
```

@@

```{r resolve Curtis1998 polytomies at random}
set.seed(111) #making it replicable
tree_random <- multi2di(tree,random=TRUE)
is.binary.tree(tree_random) #TRUE
write.tree(tree_random, file="tree_curtis1998_random.tre") #save the tree
# read.tree(file="tree_curtis1998_random.tre") #if you need to read it
```

@@

We first need to prune given branch to remove all but one species affected by polytomy. Then we can replace this species with the resolved sub-tree (Acers4sp_tree):

>>>>

```{r check Curtis1998 tree binary}
is.binary.tree(tree) #FALSE (i.e. there are polytomies)
# is.ultrametric(tree) #the tree has no branch lengths, so cant be checked
write.tree(tree, file="tree_curtis1998.tre") #save the tree
# tree <- read.tree(file="tree_curtis1998.tre") #if you need to read it
```

@@

```{r resolve Curtis1998 polytomies at random}
set.seed(111) #making it replicable
tree_random <- multi2di(tree,random=TRUE)
is.binary.tree(tree_random) #TRUE
write.tree(tree_random, file="tree_curtis1998_random.tre") #save the tree
# tree_random <- read.tree(file="tree_curtis1998_random.tre") #if you need to read it
```

@@

We first need to prune given branch from the main tree to remove all but one species affected by polytomy. Then we can replace this species with the resolved sub-tree (Acers4sp_tree):
